Capstone Movielens Report

### 2025-02-02 reports/capstone-movielens-report.Rmd
Backref citation sample1

  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

>>>>

  html_document: 
    fig_caption: true
hyperrefoptions:
  - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---
